The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-13 analysis/paper/paper.qmd
Explore topic model

emu_theses_documents |> 
  ggplot(aes(x = reorder(str_sub(document, 1, 50), gamma), y = gamma, fill = topic)) + 
  geom_bar(stat = "identity") + 
  coord_flip()

emu_theses_documents |> 
  inner_join(emu_theses |> select(title, graduation_year), by = c("document" = "title")) |> 
  ggplot(aes(x = reorder(str_sub(document, 1, 50), gamma), y = gamma, fill = topic)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  facet_wrap(~ graduation_year, ncol = 1, scales = "free", drop = TRUE)

emu_theses_documents |> 
  inner_join(emu_theses |> select(title, graduation_year), by = c("document" = "title")) |> 
  ggplot(aes(x = factor(graduation_year), y = topic, fill = factor(topic))) +
  geom_col()
```

>>>>

emu_theses_documents |> 
  ggplot(aes(x = reorder(str_sub(document, 1, 50), gamma), y = gamma, fill = topic)) + 
  geom_bar(stat = "identity") + 
  coord_flip()
```
